Human Capital Model

### 2016-02-01 Tex/paper.tex
constant and variable added

% the main section of the paper
\section{Water in the Bathtub Model}
\label{sec:human-capital-model}
Definitions of symbols employed in this paper are listed in
\textbf{Table 1}.
\begin{table}
\begin{tabular}{l|l}
  Constant & Description \\
  \hline
  $k$            &Thermal conductivity of water \\
  $\rho$         &Density of water \\
  ${\gamma}_1$   &Heat exchange coefficient between water and air \\
  ${\gamma}_2$   &Heat exchange coefficient between water and person \\
  ${\gamma}_3$   &Heat exchange coefficient between water and bathtub \\
  $C_w$          &Specific heat capacity of water \\
  $V$            &Total volume of water \\
  $x_s$          &Humidity ratio in saturated air \\
  $x_0$          &Initial humidity ratio in the air \\
  $A$            &Square of water surface \\
  $V_a$          &Volume of surrounding air \\
  $C_v$          &Evaporation heat of water \\
  $u_2$          &Temperature of person's surface \\

  Variable & Description \\
  \hline
  $u$            &Temperature of water \\
  $u_1$          &Temperature of air \\
  $u_3$          &Temperature of bathtub \\
\end{tabular}
\end{table}

>>>>

% the main section of the paper
\section{Water in the Bathtub Model}
\label{sec:human-capital-model}
Definitions of symbols employed in this paper are listed in
\textbf{Table 1}.
\begin{table}
\begin{tabular}{l|l}
  Constant & Description \\
  \hline
  $k$            &Thermal conductivity of water \\
  $\rho$         &Density of water \\
  ${\gamma}_1$   &Heat exchange coefficient between water and air \\
  ${\gamma}_2$   &Heat exchange coefficient between water and person \\
  ${\gamma}_3$   &Heat exchange coefficient between water and bathtub \\
  $C_w$          &Specific heat capacity of water \\
  $V$            &Total volume of water \\
  $v$            &Speed of air\\
  $x_s$          &Humidity ratio in saturated air \\
  $x$            &Humidity ratio in the air \\
  $x_0$          &Initial humidity ratio in the air \\
  $A$            &Square of water surface \\
  $V_a$          &Volume of surrounding air \\
  $C_v$          &Evaporation heat of water \\
  $u_2$          &Temperature of person's surface \\
  $g$            &???\\
\end{tabular}
\end{table}

\textbf{Table 2}.
\begin{table}
\begin{tabular}{l|l}
  Variable & Description \\
  \hline
  $u$            &Temperature of water \\
  $u_1$          &Temperature of air \\
  $u_3$          &Temperature of bathtub \\
  $u_h$          &Temperature of hot water from faucet \\
\end{tabular}
\end{table}
